Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-26 GWLDCII.tex
more or less through 3.17

%*****************
%Shortcuts for frequently used special characters
\newcommand{\fB}{\mathfrak{B}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\fZ}{\mathfrak{Z}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\Prop}{\textrm{Prop}}
\newcommand{\cW}{\mathcal{W}}
\newcommand{\bM}{\mathbb{M}}
\newcommand{\cZ}{\mathcal{Z}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\Dom}{\textrm{Dom}}
\newcommand{\detzr}[1] {\langle (\cZ_*^\mu|V(p))^{#1} \rangle}
\newcommand{\II}{\mathcal{I}}
\newcommand{\PP}{\mathcal{P}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\interval}[2]{[\![#1,#2]\!]}
\newcommand{\gale}[1]{\preccurlyeq_{#1}}
\newcommand{\sgale}[1]{\prec_{#1}}
\renewcommand\vec[1]{\overrightarrow{#1}}
\newcommand\cev[1]{\overleftarrow{#1}}
%*****************

@@

\begin{equation} C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
0  & \textrm{ if } q \not \in V(p)  \end{cases}
\;. \label{C(W) dfn}\end{equation} \todo{Change $c_{p,q}$ to $x_{p,q}$ to be consistent}

The entries $c_{p,q}$ are non-zero real variables. Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with. See Example~\ref{integraldetails} for an example of a diagram $W$ and its associated matrix.

@@

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}. The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}c_{p_r}}{R(W)} \;, \end{equation}
where the denominator $R(W)$ is given in Definition~\ref{def R(W)} below. The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.

@@

\begin{dfn}\label{def R(W)}
Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$. Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise orderin. That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to vertex $e+1$). Define the polynomial
\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
to be the component of $R(W)$ associated to edge $e$. Note that if $r = 1$ (i.e. there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = c_{p,e} c_{p,e+1}$. If $r=0$, set $R_e = 1$. The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e. 
\[R(W) = \prod_{e \in V} R_e.\]
\end{dfn}

@@

\begin{eg} \label{integraldetails}
Consider the admissible Wilson loop diagram 
\[W = \big(\{(1,4), (2,4), (5,7), (5,8)\},[8]\big),\]
from Figure~\ref{fig:ex of WLD}. Ordering the propagators as listed above, we obtain the associated matrix
\[ C(W) = \left(
\begin{array}{cccccccc}
c_{1,1} & c_{1,2} & 0 & c_{1,4} & c_{1,5} & 0 & 0 & 0 \\
0 & c_{2,2} & c_{2,3} & c_{2,4} & c_{2,5} & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & c_{3,5} & c_{3,6} & c_{3,7} & c_{3,8} \\
c_{4,1} & 0 & 0 & 0 & c_{4,5} & c_{4,6} & 0 & c_{4,8}  \\
\end{array}
\right) \;.\]

To calculate $R(W)$, we first compute the polynomials associated to each edge of $W$: \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram (recall equation~\eqref{eq:omega(W) def}) is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,2}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,8}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \eas
\end{eg}

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$;  $X$ is still admissible since we have not decreased the support of any set of propagators. 
% From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
It follows from the position of $q$ in $X$ that $I_j^X(q) = j$, and from Lemma~\ref{lem no fourth vertex} that $I_{j+1}^X(q) \neq j$. By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$; in particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.

@@

\begin{thm}\label{res:alg gives GN}
The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is a Grassmann necklace.
\end{thm}
\begin{proof}
\note{Sian replaced ``counterclockwise'' with ``clockwise'' in a couple of places in this proof: someone please doublecheck?  Karen checked and it seems correct with Sian's changes.}
For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$. By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$. We prove that $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is equivalent to the definition of Grassmann necklace given in Definition~\ref{def:grassmann necklace}.

Suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.  Fix $n$.  Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators. %, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.

@@

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.  If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the previous equality remains true, albeit vacuously.  Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$. Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.  This also implies that $m\geq_i b+1$.

@@

By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$). The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.  This gives the equations
\begin{align*}
  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
\end{align*} 
where the diagram is indicated in the superscript.
Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.

@@

\begin{thm}\label{res alg gives correct GN}
The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
\end{thm}

\begin{proof}
We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$. Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show: 
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: the algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

>>>>

%*****************
%Shortcuts for frequently used special characters
\newcommand{\fB}{\mathfrak{B}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\fZ}{\mathfrak{Z}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\Prop}{\textrm{Prop}}
\newcommand{\cW}{\mathcal{W}}
\newcommand{\bM}{\mathbb{M}}
\newcommand{\cZ}{\mathcal{Z}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\Dom}{\textrm{Dom}}
\newcommand{\detzr}[1] {\langle (\cZ_*^\mu|V(p))^{#1} \rangle}
\newcommand{\II}{\mathcal{I}}
\newcommand{\PP}{\mathcal{P}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\interval}[2]{[\![#1,#2]\!]}
\newcommand{\gale}[1]{\preccurlyeq_{#1}}
\newcommand{\sgale}[1]{\prex_{#1}}
\renewcommand\vec[1]{\overrightarrow{#1}}
\newcommand\cev[1]{\overleftarrow{#1}}
%*****************

@@

\begin{equation} C(W)_{p,q} = \begin{cases} x_{p,q} & \textrm{ if } q \in V(p) \\
0  & \textrm{ if } q \not \in V(p)  \end{cases}
\;. \label{C(W) dfn}\end{equation}

The entries $x_{p,q}$ are non-zero real variables. Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with. See Example~\ref{integraldetails} for an example of a diagram $W$ and its associated matrix.

@@

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}. The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation}
where the denominator $R(W)$ is given in Definition~\ref{def R(W)} below. The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.

@@

\begin{dfn}\label{def R(W)}
Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$. Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise orderin. That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to vertex $e+1$). Define the polynomial
\[ R_e =  x_{p_1,e+1} \prod_{j= 1}^{r-1} \left((x_{p_j,e} x_{p_{j+1},e+1} - x_{p_{j+1},e} x_{p_{j},e+1} ) \right) x_{p_r,e}\;\]
to be the component of $R(W)$ associated to edge $e$. Note that if $r = 1$ (i.e. there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = x_{p,e} x_{p,e+1}$. If $r=0$, set $R_e = 1$. The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e. 
\[R(W) = \prod_{e \in V} R_e.\]
\end{dfn}

@@

\begin{eg} \label{integraldetails}
Consider the admissible Wilson loop diagram 
\[W = \big(\{(1,4), (2,4), (5,7), (5,8)\},[8]\big),\]
from Figure~\ref{fig:ex of WLD}. Ordering the propagators as listed above, we obtain the associated matrix
\[ C(W) = \left(
\begin{array}{cccccccc}
x_{1,1} & x_{1,2} & 0 & x_{1,4} & x_{1,5} & 0 & 0 & 0 \\
0 & x_{2,2} & x_{2,3} & x_{2,4} & x_{2,5} & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & x_{3,5} & x_{3,6} & x_{3,7} & x_{3,8} \\
x_{4,1} & 0 & 0 & 0 & x_{4,5} & x_{4,6} & 0 & x_{4,8}  \\
\end{array}
\right) \;.\]

To calculate $R(W)$, we first compute the polynomials associated to each edge of $W$: \bmls R_1 = x_{1,1} x_{1, 2}\quad R_2 = x_{2,2} x_{2,3} \quad R_4 = x_{2,5} (x_{2,4}x_{1,5} - x_{2,5}x_{1,4})x_{1,4} \\ R_5 = x_{4,6} (x_{4,5}x_{3,6} - x_{3,5}x_{4,6})x_{3,5} \quad R_7 = x_{3,7} x_{3,8} \quad R_8 = x_{4,8} x_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram (recall equation~\eqref{eq:omega(W) def}) is \bas \Omega(W) = \frac{\textrm{d}x_{1,1}\textrm{d}x_{1,2}\textrm{d}x_{1,4}\textrm{d}x_{1,5}\textrm{d}x_{2,2}\textrm{d}x_{2,3}\textrm{d}x_{2,4}\textrm{d}x_{2,5}\textrm{d}x_{3,5}\textrm{d}x_{3,6}\textrm{d}x_{3,7}\textrm{d}x_{3,8}\textrm{d}x_{4,5}\textrm{d}x_{4,6}\textrm{d}x_{4,8}\textrm{d}x_{4,1}}{x_{1,1} x_{1, 2}x_{2,2} x_{2,3}x_{2,5} (x_{2,4}x_{1,5} - x_{2,5}x_{1,4})x_{1,4}x_{4,6} (x_{4,5}x_{3,6} - x_{3,5}x_{4,6})x_{3,5}x_{3,7} x_{3,8}x_{4,8} x_{4,1}} \;. \eas
\end{eg}

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. \hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}? If so, the entire proof depends on this fact. We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \hlfix{is assigned to}{was this the one place where we has agreed to keep assigned instead of contributes?} a vertex {\color{violet} in the diagram $V$}, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

\sanote{skipping careful read of this proof and moving on}
Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$;  $X$ is still admissible since we have not decreased the support of any set of propagators. 
% From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
It follows from the position of $q$ in $X$ that $I_j^X(q) = j$, and from Lemma~\ref{lem no fourth vertex} that $I_{j+1}^X(q) \neq j$. By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$; in particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.

@@

\begin{thm}\label{res:alg gives GN}
The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is a Grassmann necklace.
\end{thm}
\begin{proof}
%\note{Sian replaced ``counterclockwise'' with ``clockwise'' in a couple of places in this proof: someone please doublecheck?  Karen checked and it seems correct with Sian's changes.}
For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$. By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$. We prove that $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is equivalent to the definition of Grassmann necklace given in Definition~\ref{def:grassmann necklace}.

Suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.  Fix $n$.  Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices \hlfix{which is minimal with respect to the number of propagators}{minimal in what respect? $i$ first where this occurs? $m$ the smallest such number? what do propagators have to do with it?}. %, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.

@@

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is \bas I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]\eas {\color{violet}by Remark \ref{rmk algorithm locally same}}.  If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the above equality remains true, albeit vacuously.  Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.  Consequently, by Remark \ref{clockwise ordering rem}, in building $I_{i+1}$,  when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, \st{since the same propagators have been assigned beforehand.}\sanote{don't like same here}{\color{violet}since any propagators lying counterclockwise of $p$ on the edge $i-1$ must have their support in $[i-1, b]$. By Lemma \ref{no fourth vertex}, these propagators contribute before the algorithm reaches $b$. Furthermore, Remark  \ref{rmk algorithm locally same} implies that these propagators contribute the same vertices to both $I_i$ and $I_{i+1}$.} This also implies that $m\geq_i b+1$.

@@

\st{By the above observations, if we commence Algorithm {\ref{alg:put GN on WLD}} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$).} {\color{violet} Note that the propagators in $\cP_{out}(p,<_i)$ come first in the ordering imposed by $I_i^W$ (Definition \ref{proporderingdfn}). Therefore, the ordering and contributions of propagators defined by $I_b^{W'}$ are the same as that of $I_i^W$ after the removal of these initial propagators.} \st{The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.}  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.  This gives the equations
\begin{align*}
  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
\end{align*} 
\st{where the diagram is indicated in the superscript.}
Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.\sanote{see previous question about minimality. not sure why this is true, unless minimality in $|[i,m]|$?.}

@@

Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann Neclace for $M(W)$.

\begin{thm}\label{res alg gives correct GN}
The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
\end{thm}
\sanote{skipping reading of this for now}
\begin{proof}
We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$. Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show: 
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: the algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

\sanote{START HERE}
